\documentclass[11pt,twoside,a4paper]{article}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1} %
}

\usepackage{enumitem}
\usepackage{geometry}

\newgeometry{vmargin={15mm}, hmargin={15mm}}   % set the margins

\renewcommand{\familydefault}{\sfdefault} % change font
\setcounter{secnumdepth}{0}

\usepackage{hyperref}

\usepackage{xcolor}
\hypersetup{%
  colorlinks=true,% hyperlinks will be coloured
  %linkcolor=green,% hyperlink text will be green
  %linkbordercolor=red,% hyperlink border will be red
  %filecolor=blue,
  urlcolor=blue
}

\makeatletter
\renewcommand\maketitle
{\noindent
 {\textbf{Üsküdar, Istanbul, Turkey}}%
 \medskip\par\noindent
 {\textbf{linkedin.com/in/onur-ovali}}%
 \hfill
 {\large\@date}%
 \bigskip\par\noindent
}

\title{Onur Ovalı}
\author{Onur Ovalı}
\date{\today}

\begin{document}

  %\maketitle

  %\noindent\textbox{
  %  \small\begin{tabular}[c]{l}
  %    Üsküdar, Istanbul, Turkey \\
  %    +90 507 841 5086
  %  \end{tabular}
  %}\hfill%
  %\noindent{
  %  \Large\bfseries\begin{tabular}[c]{c}
  %    ONUR OVALI
  %  \end{tabular}
  %}\hfill%
  %\noindent{
  %  \small\begin{tabular}[c]{r}
  %    linkedin.com/in/onur-ovali/ \\
  %    %github.com/jnuo/ \\
  %    onurovalii@gmail.com
  %  \end{tabular}
  %}

  \noindent\textbox{Üsküdar, Istanbul, Turkey \\+90 507 841 5086\hfill}
  \textbox{\hfil\Large\bfseries ONUR OVALI\hfil}
  \textbox
    {\hfill \begin{tabular}[c]{r}
      linkedin.com/in/onur-ovali/ \\
      %github.com/jnuo/ \\
      onurovalii@gmail.com
    \end{tabular}
    }

  \hrule

  \section{Summary}
    Product manager based in Istanbul w/ 10 years of product development experience (5 years - software development \& 5 years - product management), all in online products. CS graduate with an MBA. Interested in digital product management based on customer insights (data analysis and customer interviews) in agile teams/companies.

  \section{Employment}
    \subsection{\noindent\textbox{Head of Product Management\hfill}\textbox{\hfil Kariyer.net\hfil}\textbox{\hfill May 2019 - Present}}
      Managed the product team of 8 PMs, responsible for \href{https://www.kariyer.net/}{Kariyer.net Job Board (B2C)}, \href{https://ats.kariyer.net/#/}{Kariyer.net Applicant Tracking System (B2B)} and \href{https://www.isinolsun.com/}{İşin Olsun (blue collar job board \& ATS)} and micro products like \href{https://www.iskolig.com/}{iskolig.com} \& \href{http://www.hrvenue.com/}{HRVenue.com}.\\
      $\bullet$ Managed the \textbf{relationships} with internal \& external \textbf{shareholders} allowing the POs to focus on their tasks. \\
      $\bullet$ Improved each POs skills and knowledge w/ continous educations, performance management practices and 1-1 meetings, \textbf{developed autonomous and confident product managers} who can make \textbf{strategical decisions}.\\
      $\bullet$ High-valued customers' big problem was \textbf{irrelavant candidates}. Designed new products/services like Smart Job Ads (suggesting best-fitting candidates w/out application), Express Search (detailed search functionality), Assessment Tests Marketplace (local test providers sell their tests inside ATS). These new modules decreased the number of complaints and also increased non-essential products' \textbf{revenue by 40\%}.\\
      $\bullet$ Changed the \textbf{UX} flow of the \textit{posting a job ad} process and \textbf{increased job ad details by 30\%}\\
      $\bullet$ Designed an \textbf{open API} to add 4 new modules (Assessment Marketplace, Video Interviews, KVKK (GDPR) \& Survey Modules) with the same UX \& data flow and \textbf{saved on development} source (1 int. instead of 15).\\
      $\bullet$ Re-designed company profiles on the job-board w/ the CMS on the ATS. The company profiles' \textbf{traffic tripled}. \\
      $\bullet$ Designed a \textbf{personalized} Profile page, offering relevant content for logged in candidates. Resulted in 40\% increase on the ratio of updating resume and 30\% increase on the users who view a job ad page after login.\\
      $\bullet$ Lead the \textbf{data science} team on converting all static and rule-based processes into \textbf{data-driven models}.
    \subsection{\noindent\textbox{Product \& Marketing Manager\hfill}\textbox{\hfil Turna.com\hfil}\textbox{\hfill Dec 2017 - Apr 2019}}
      Managed product analytics and performance marketing for \href{https://www.turna.com/}{Turna.com} - an e-commerce platform for flight tickets.\\
      $\bullet$ Created \textbf{automated funnel reports} for each channel (apps \& web), used for \textbf{conversion rate optimization}. Decreased payment errors by 15\% and increased total \textbf{conversion rate by 30\%}.\\
      $\bullet$ Created automated ROI \& P\&L reports for campaigns, optimized budget allocations. Improved \textbf{ROI by 90\%}.\\
      $\bullet$ Created \textbf{customer lifetime value} (LTV) report, interviewed top 50 customers. Discovered new segments with \textbf{insights gained}. Designed new campaigns and \textbf{attracted new customers with high LTV}.\\
      $\bullet$ Defined \textbf{behavioral segments} and run email marketing campaigns. Achived better results (\textbf{higher conversion rates} and \textbf{lower CPAs}) than paid campaigns. Thus, designed an \textbf{inbound marketing automation project} which became an R\&D project supported by government due to its improvement models with \textbf{Machine Learning}.
    \subsection{\noindent\textbox{Technical Product Manager\hfill}\textbox{\hfil Biletbank.com\hfil}\textbox{\hfill Aug 2015 - Aug 2017}}
      Led the microservices transformation project for \href{https://biletbank.com}{B2B online travel agency} (\textbf{SaaS} product).\\
      $\bullet$ Software was in \textbf{monolithic} architecture. Started the microservices transformation project. Created the \textbf{architecture of all services' interfaces} and the \textbf{database designs}.\\
      $\bullet$ Analyzed \textbf{business requirements}, created \textbf{user stories}, designed new \textbf{data structures} and processes.\\
      $\bullet$ Defined the \textbf{MVP}, planned the project, created \& prioritized tasks and managed the \textbf{backlog}.\\
      $\bullet$ By implementing \textbf{branching} and \textbf{automatic deployment}; solved productivity problems of development team.\\
      $\bullet$ Presented \textbf{Scrum \& Agile} to the team, convinced using them and \textbf{increased efficiency}. Managed development \& synch. of multiple teams and products with \textbf{Lean Startup} methodology; met deadlines and project targets.
    \subsection{\noindent\textbox{Software Developer / Analyst\hfill}\textbox{\hfil T. İş Bankası A.Ş.\hfil}\textbox{\hfill Nov 2010 - Aug 2015}}
      Full-stack developer for \href{https://www.isbank.com.tr/internet/}{Isbank Internet Branch} - one of the biggest private banks in Turkey.\\
      $\bullet$ Developed \textbf{web services} for 2 factor authentication methods including OTP generators and iOS Touch ID.\\
      $\bullet$ Performed \textbf{bug tracking} for internet branch, coordinating work of multiple teams with an SLA for open bugs.\\
      $\bullet$ Supported \textbf{IT Security} team with \textbf{Intrusion Detection Tests}, after passing \textbf{ISACA CISA June 2012} exam.
  \section{Education}
    \subsection{\noindent\textbox{MBA\hfill}\textbox{\hfil Koç University, Istanbul\hfil}\textbox{\hfill Sep 2015 - Dec 2017}}
      $\bullet$ General MBA Program with a focus on innovation management, entrepreneurship \& marketing.\\
      $\bullet$ International attendance:\\
        \indent{\textsection{ IE Business School, Madrid, Spain: Sales \& Marketing (Erasmus Program)\hfill Aug-Dec 2017}}\\
        \indent{\textsection{ Hitotsubashi ICS, Tokyo, Japan: Innovation X Globalisation: Japan Style\hfill Mar 2017}}\\
        \indent{\textsection{ IE Business School, Madrid, Spain: High Tech Entrepreneurship (online course)\hfill Jan-Mar 2017}}\\
        \indent{\textsection{ Yale SOM, New Haven, USA: Behavioral Economis, Marketing \& Finance\hfill Oct 2016}}
    \subsection{\noindent\textbox{BSc in Computer Engineering\hfill}\textbox{\hfil METU, Ankara\hfil}\textbox{\hfill Sep 2005 - Jul 2010}}
      $\bullet$ Bachelor's Degree on Computer Science Program with a focus on algorithms, OOP \& AI.
  \section{Certifications}
    $\bullet$ Deeply Practical Project Management issued by Udemy. Credential ID: UC-LCHJ8SAA\hfill Sep 2018\\
    $\bullet$ Advanced Google Analytics Certificate issued by GA Academy. Credential ID: 234472174\hfill Aug 2018\\
    $\bullet$ ISACA CISA (Certified Information System Auditor). Exam passed, certification not received. \hfill Jun 2012
  \section{Skills, Knowledge \& Tools}
    \subsection{Product Management}
      $\bullet$ Experience on product strategy, market analysis, growth, benchmarking, product analytics \& user interviews.\\
      $\bullet$ Worked on many sides of \textbf{product development life cycle} in different \textbf{agile (scrum) teams/companies}.\\
      $\bullet$ Experienced on \textbf{user stories}, \textbf{flow diagrams} w/ detailed \textbf{case analysis}; allowing \textbf{simple \& clear briefs} for design (UX/UI professionals) \& development teams.\\
      $\bullet$ \textbf{Prioritization, backlog \& shareholder relations} management is an everyday task.
    \subsection{Analytics \& Digital Marketing}
      $\bullet$ Advanced knowledge on analytics tools \textbf{Google Analytics}, \textbf{Datastudio}, \textbf{GTM}, \textbf{Firebase} \& Kochava.\\
      $\bullet$ Advanced on managing \textbf{performance campaigns}: segmentation, reporting \& optimization.\\
      $\bullet$ Hands on reporting experience on \textbf{Google Ads}, \textbf{FB Business Mng} \& \textbf{Criteo}.\\
      $\bullet$ Advanced knowledge on office programs (Excel, Powerpoint, etc.).
    \subsection{Computer Science}
      $\bullet$ Deep knowledge on \textbf{SQL} with professional experience on \textbf{T-SQL} \& \textbf{Microsoft SQL Server}.\\
      $\bullet$ Advanced knowledge on \textbf{CS basics}: \textbf{Algorithms}, Data Structures, Database \& web services design.\\
      $\bullet$ Professional coding experience on \textbf{Python} \& \textbf{C\#}, basic knowledge on Java, C++.\\
      $\bullet$ Best practices of \textbf{RDBMS} \& \textbf{NoSQL} (Couchbase, MongoDB) usage.\\
      $\bullet$ Basic knowledge on cloud computing on AWS \& cost optimization.
    \subsection{Languages}
      Native in \textbf{Turkish}, fluent in \textbf{English}, intermediate in \textbf{Spanish}.\\

    \hfill written in \LaTeX

\end{document}
